\Large Feature and order manipulations in a free recall task affect memory for current and future lists

### 2023-11-13 paper/main.tex
added note on pnr curves

Probability of first recall curves~\citep{AtkiShif68, PostPhil65, WelcBurn24}
reflect the probability that an item will be recalled first, as a function of
its serial position during encoding. To carry out this analysis, we initialized
(for each participant) a number-of-lists (16) by number-of-words-per-list (16)
matrix of 0s. Then, for each list, we found the index of the word that was
recalled first, and we filled in that position in the matrix with a 1. Finally,
we averaged over the rows of the matrix to obtain a 1 by 16 array of
probabilities, for each participant. We used an analogous procedure to compute
probability of $n$\textsuperscript{th} recall curves for each participant.
Specifically, we filled in the corresponding matrices according to the
$n$\textsuperscript{th} recall on each list that each participant made. When a
given participant had made fewer than $n$ recalls for a given list, we simply
excluded that list from our analysis when computing that participant's
curve(s). The probability of first recall curve corresponds to a special case
where $n = 1$.

>>>>

Probability of first recall curves~\citep{AtkiShif68, PostPhil65, WelcBurn24}
reflect the probability that an item will be recalled first, as a function of
its serial position during encoding. We used an analogous approach to compute
the proportion of trials on which each item (as a function of its presentation
position) was recalled at output position $n$~\citep{HowaKaha99, PolyEtal09,
ZhanEtal23}. To carry out this analysis, we initialized (for each participant)
a number-of-lists (16) by number-of-words-per-list (16) matrix of 0s. Then, for
each list, we found the index of the word that was recalled first, and we
filled in that position in the matrix with a 1. Finally, we averaged over the
rows of the matrix to obtain a 1 by 16 array of probabilities, for each
participant. We used an analogous procedure to compute probability of
$n$\textsuperscript{th} recall curves for each participant. Specifically, we
filled in the corresponding matrices according to the $n$\textsuperscript{th}
recall on each list that each participant made. When a given participant had
made fewer than $n$ recalls for a given list, we simply excluded that list from
our analysis when computing that participant's curve(s). The probability of
first recall curve corresponds to a special case where $n = 1$.

We note that several other studies have used a slightly different approach to
compute these curves, by correcting for the ``availability'' of a given word to
be recalled. For example, if a participant recalls item 1, then item 2 on a
given list, our approach places a 0 into the item 1 column for that list when
computing the ``probability of second recall'' curve. However, accounting for
the fact that the participant had already recalled item 1, an alternative
approach~\citep[e.g.,][]{Farr10} would be to count the item 1 column as
``unobserved'' (i.e., missing data). Ultimately we chose to use the simpler
variant of this approach in our work, but we direct the reader to further
discussion of this issue in other work~\citep{MoraGosh14, Farr14}.
